Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-03 manuscript.Rmd
Edits to intro

Disentangling the complicated relationship between mass online
mobilization---and social mobilization in person---continues to be relevant,
even as our modes of communication change. The political events that
transpired during and after the Arab Spring are still in the process of being
understood. As Zeitzoff [-@zeitzoff2017social] recognizes, social media is
changing conflict, but the mechanisms and relationships by which it does so are
still being understood.

@@

Citizens communicate with each other with increased transparency due to the
ubiquitous availability of social media such as low-cost and egalitarian
platforms like Twitter. Citizens are able to access these tools via mobile
phones and computers with Internet connectivity, providing a stream of real-time
shared information. Citizens can share the location of events like protests and
military incursions, the degree of state repression, and the number of
casualties. In turn, the government---interested in remaining in
power---monitors social media platforms to ascertain emerging threats
[@comninos2011twitter], such as where new groups are forming and where existing
groups are strengthening, where gatherings are held, and who the idea
entrepreneurs are.

@@

People join social and political resistance movements because they feel a sense
of connection to the cause and because they have been sufficiently convinced to
participate. Given that people are generally risk-averse, overcoming inertia
requires a strong connection to the group identity or a strong aversion to an
individual, event, or political injustice [@goldstone1980theories;
@goldstone2011understanding]. Political resistance offers participants the
opportunity to “lose themselves” and relinquish their individual identity in
favor of identification with a larger group identity, contributing to a cohesive
group ready and mobilized for action [@Hoffer2011true].

Previous research on social movements supports the idea that participants are
likely to join movements when they know and have a personal connection to
someone else already involved [@mcadam1986recruitment]. The type of collective
contentious behavior that manifests in society is a function of the available
political opportunity structures. The political opportunity structure are
“comprised of *(sic)* specific configuration of resources, institutional
arrangements and historical precedents for social mobilization, which facilitate
the development of protest movements in some instances and constrain them in
others” [@kitschelt1986political]. What emerges as strategies and tactics in
contentious politics are, in essence, a function of what the system makes
possible. This includes the number of people and their disposition (i.e.
nonviolent or violent), as well as their internal structure. The more cohesive a
group is, the greater threat they pose to the establishment.

Cohesion is also a familiar concept in the study of civil conflicts, as it
pertains to group affiliation and the ability to overcome collective action
problems. Individuals must act in concert---that is, cohesively---to
accomplish the task of challenging the authority of the state [@olson1965logic;
@eisinger1973conditions; @tilly2004contentious; @francisco1995relationship].
Recent work has considered rebel recruitment for participation in
civil conflicts as a function of internal cohesion [@gates2002recruitment]:
Rebel movement success is influenced by the degree of group cohesion, which
itself is a function of geographic distance, ideology, and ethnicity.
Within Syria, multiple rebel groups within Syria exist, sourcing fighters locally
from the disaffected Syrian population and internationally through
fighters from transnational terrorist organizations. There is considerable
intergroup competition for participation in the rebel movement and
punishment for defectors for nonparticipation [@gates2002recruitment].
Foreign fighters would appear to be amply motivated to fight, given their
decision to relocate from a home country that may be located in the region
or much farther away.

>>>>

Disentangling the complicated relationship between mass online
mobilization---and social mobilization in person---continues to be relevant,
even as our modes of communication change. The political events that
transpired during and after the Arab Spring are still in the process of being
understood. As Zeitzoff [-@zeitzoff2017social] recognizes, social media is
changing conflict, but the mechanisms and relationships by which it does so are
still largely unknown.

@@

Citizens communicate with each other with increased transparency due to the
ubiquitous availability of social media such as low-cost and egalitarian
platforms like Twitter. Citizens are able to access these tools via mobile
phones and computers with Internet connectivity, providing a stream of real-time
shared information. Citizens can share the location of events like protests and
military incursions, the degree of state repression, and the number of
casualties. In turn, the government---interested in remaining in
power---monitors social media platforms to ascertain emerging threats
[@comninos2011twitter], such as where new groups are forming, where existing
groups are strengthening, where gatherings are held, and who the idea
entrepreneurs are.

@@

People join social and political resistance movements because they feel a sense
of connection to the cause. Given that people are generally risk-averse, overcoming inertia
requires a strong connection to the group identity or a strong aversion to an
individual, event, or political injustice [@goldstone1980theories;
@goldstone2011understanding]. Political resistance offers participants the
opportunity to “lose themselves” and relinquish their individual identity in
favor of identification with a larger group, contributing to a cohesive
group ready and mobilized for action [@Hoffer2011true].

Previous research on social movements supports the idea that participants are
more likely to join movements when they know and have a personal connection to
someone else already involved [@mcadam1986recruitment]. The type of collective
contentious behavior that manifests in society is a function of the available
political opportunity structures. The political opportunity structure are
“comprised of *(sic)* specific configurations of resources, institutional
arrangements and historical precedents for social mobilization, which facilitate
the development of protest movements in some instances and constrain them in
others” [@kitschelt1986political]. What emerges as strategies and tactics in
contentious politics are, in essence, a function of what the system makes
possible. This includes the number of people and their disposition (i.e.
nonviolent or violent), as well as their internal structure. The more cohesive a
group is, the greater threat they pose to the establishment.

Cohesion is also a familiar concept in the study of civil conflicts, as it
pertains to group affiliation and the ability to overcome collective action
problems. Individuals must act in concert---that is, cohesively---to
accomplish the task of challenging the authority of the state [@olson1965logic;
@eisinger1973conditions; @tilly2004contentious; @francisco1995relationship].
Recent work has considered rebel recruitment for participation in
civil conflicts as a function of internal cohesion [@gates2002recruitment]:
Rebel movement success is influenced by the degree of group cohesion, which
itself is a function of geographic distance, ideology, and ethnicity.
Within Syria, multiple rebel groups exist, sourcing fighters locally
from the disaffected Syrian population and internationally through
fighters from transnational terrorist organizations. There is considerable
intergroup competition for participation in the rebel movement and
punishment for defectors for nonparticipation [@gates2002recruitment].
Foreign fighters would appear to be amply motivated to fight, given their
decision to relocate from a home country that may be located in the region
or much farther away.
